Supplementary Material for Asymmetry paper

### 2020-07-09 Supplementary/Sup_mat.Rmd
updates to figures

```{r HoopSizeFacets, include=T, echo=F, fig.width = 10, fig.height = 10, fig.cap = "_Facet plots for the Hoop Size experiment_"}
load("../Analyses/Experiment_3_Hoop_size/scratch/df_part2_norm")
df_hoopsize <- norm_dat
rm(norm_dat)

@@

``` {r TwoThrowFacets, include = T, echo = F, fig.width = 10, fig.cap = "_Facet plots for each participant in the Two Throw experiment_"}
# process 
df_TwoThrow <- model_data_pos %>% 
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(HoopDelta)),
         slab_measures = factor(temp, labels = c("~90%", "~50% - 1", "~50%", "~50% + 1", "~50% + 2", "~10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(HoopDelta))

@@

# plt_difference 
plt_difference <- draws$Plots[3][[1]] + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  scale_x_continuous("Difference: One throw - Two throw") +
  guides(fill = guide_legend(title = "Distance"),
         colour = guide_legend(title = "Distance"))

@@

```{r TwoThrowPlts, include = T, echo = F, fig.asp = .65, fig.cap = "_The left hand plots show the Prior preditcions for the Two Throw experiment. The right hand plots show the Posterior predictions for the Two Throw expeirment._"}
# get legend 
TwoThrowLegend <- g_legend(priors_plt)

grid.arrange(arrangeGrob(priors_plt + theme(legend.position = "none"), plt_examples + theme(legend.position = "none")),
                     TwoThrowLegend, heights=c(10, 1))

@@

This effect was the strongest for the closest separation which reflects the larger amount of variation in standing position with distance in the Two-throw condition (Figure \@ref(fig:TwoThrowPlts). In general, when in the One-throw condition, participants stood further from the centre (mean of `r round(mu_close[1], digits = 3)`, 95% HPDI of |`r round(lower_close[1], digits = 3)` , `r round(upper_close[1], digits = 3)`|) than in the the Two-throw condition (mean of `r round(mu_close[1], digits = 3)`, 95% HPDI of |`r round(lower_close[1], digits = 3)` , `r round(upper_close[1], digits = 3)`|) with P(One-throw > Two_throw|data) = `r paste(P_close$above0*100, "%", sep = "")`.

@@

``` {r RewardFacets, include = T, echo = F, fig.asp = .75, fig.cap = "_Facet plots for the Rewards experiment_"}
df_Rewards <- model_data %>%
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(Norm_Delta)),
         slab_measures = factor(temp, labels = c("90%", "75%", "25%", "10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(Norm_Delta))

@@

@@

```{r PltRewardestimates, echo = F, include = T, warning = F, fig.asp=.75, fig.cap="_Posterior distributions for the Reward Study_"}
gridExtra::grid.arrange(plt_dist, bottom, heights = c(2, 4))
```

>>>>

```{r HoopSizeFacets, include=T, echo=F, fig.width = 10, fig.height = 10, fig.cap = "_Each facet of this plot shows were each participant stood on each trial. The x-axis shows the different distances that participants were tested at with 0 being the point at which they were closest 50% from the centre. The y-axis shows the normalised standing position between the Big Hoop and the Small Hoop. _"}
load("../Analyses/Experiment_3_Hoop_size/scratch/df_part2_norm")
df_hoopsize <- norm_dat
rm(norm_dat)

@@

``` {r TwoThrowFacets, include = T, echo = F, fig.width = 10, fig.cap = "_Each facet of this plot shows the stnading position on each trial and condition for each participant. The x-axis shows the different distances that participants were tested at with 0 being the point at which they were closest 50% from the centre. The y-axis shows the normalised standing position (between the centre point and one of the two side hoops)._"}
# process 
df_TwoThrow <- model_data_pos %>% 
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(HoopDelta)),
         slab_measures = factor(temp, labels = c("~90%", "~50% - 1", "~50%", "~50% + 1", "~50% + 2", "~10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(HoopDelta))

@@

# plt_difference 
plt_difference <- draws$Plots[3][[1]][["data"]] %>%
  mutate(Dist_type = as.factor(Dist_type)) %>%
  mutate(Dist_type = factor(Dist_type, c("Close", "Mid", "Far"))) %>% 
  ggplot(aes(diff,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  # see::scale_color_flat() + 
  # see::scale_fill_flat() + 
  scale_fill_viridis_d() + 
  scale_colour_viridis_d() +
  scale_x_continuous("Difference: One throw - Two throw") +
  guides(fill = guide_legend(title = "Distance"),
         colour = guide_legend(title = "Distance"))

@@

```{r TwoThrowPlts, include = T, echo = F, fig.asp = .65, fig.cap = "_The panel shows the Prior preditcions for the Two Throw experiment. The middle panel shows the Posterior predictions for the Two Throw expeirment. The bottom panel shows the difference between One and Two throw conditions across the same distances shown in the other panels_"}
# get legend 
TwoThrowLegend <- g_legend(priors_plt)

grid.arrange(arrangeGrob(priors_plt + theme(legend.position = "none"), plt_examples + theme(legend.position = "none")),
                     TwoThrowLegend, plt_difference, heights=c(10, 1, 5))

@@

This effect was the strongest for the closest separation which reflects the larger amount of variation in standing position with distance in the Two-throw condition (Figure \@ref(fig:TwoThrowPlts). In general, when in the One-throw condition, participants stood further from the centre (mean of `r round(mu_close[1], digits = 3)`, 95% HPDI of |`r round(lower_close[1], digits = 3)` , `r round(upper_close[1], digits = 3)`|) than in the the Two-throw condition (mean of `r round(mu_close[1], digits = 3)`, 95% HPDI of |`r round(lower_close[1], digits = 3)` , `r round(upper_close[1], digits = 3)`|) with P(One-throw > Two_throw|data) = `r paste(P_close$above0*100, "%", sep = "")`. However, as can be seen in \@ref(fig:TwoThrowPlts), the difference is generally small which and consitent across all distances. This means that when participants were given the opportunity to throw to both hoops (i.e., in the Two throw condition), they were still suboptimal in their performance.

@@

``` {r RewardFacets, include = T, echo = F, fig.asp = .75, fig.cap = "_Each facet in this plot shows the decision on a single trial about where to stand and how the participant had opted to split the reward. The x-axis corresponds to the participants chance of success had they stood at the centre with the y-axis showing the normalised standing potision._"}
df_Rewards <- model_data %>%
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(Norm_Delta)),
         slab_measures = factor(temp, labels = c("90%", "75%", "25%", "10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(Norm_Delta))

@@

The priors for this model were set to be roughly flat and uniformative to reflect the uncertainty around the outcomes of this experiment. Until this experiment, we had not run a version of this task in which the different targets could have different value associtated with them.

@@

```{r PltRewardestimates, echo = F, include = T, warning = F, fig.asp=.45, fig.cap="_This plot shows the posterior distribution of standing positions for the Reward study_"}
# gridExtra::grid.arrange(plt_dist, bottom, heights = c(2, 4))
plt_inter
```
